Self Regulation Ontology Retest Analyses

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd

```{r}
test_data_522 %>%
  select(ez_contrast_vars$dv) %>%
  gather(key, value) %>%
  group_by(key) %>%
  summarise(tvals = get_tval(value), 
            means = get_mean(value))
```

Means and and T values comparing the means to 0 for T2 data.

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  gather(key, value) %>%
  group_by(key) %>%
  summarise(tvals = get_tval(value), 
            means = get_mean(value))
```

```{r message=FALSE, warning=FALSE}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  mutate(time = "Time 1") %>%
  bind_rows(test_data %>%
              select(ez_contrast_vars$dv) %>%
              mutate(time = "Time 2")) %>%
  gather(key, value, -time) %>%
  rename(dv = key) %>%
  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
  ggplot(aes(value))+
  geom_density(aes(group=dv, col=rt_acc), linetype="dotted")+
  geom_density(aes(col=rt_acc), size=2.5)+
  xlim(-1.5,1.5)+
  geom_vline(xintercept=0, linetype="dashed", size=1.5)+
  theme(legend.title=element_blank())+
  xlab("")+
  ylab("")+
  facet_wrap(~time)
```

@@

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  mutate(time = "Time 1") %>%
  bind_rows(test_data %>%
              select(ez_contrast_vars$dv) %>%
              mutate(time = "Time 2")) %>%
  gather(key, value, -time) %>%
  rename(dv = key) %>%
  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
  group_by(rt_acc, time) %>%
  summarise(tvals=get_tval(value),
            means=get_mean(value))
```

### Are their reliabilities >0?

Although the thresholds and non-decision times for contrasts are >0 still have low reliabilities.

```{r  message=FALSE, warning=FALSE}
rt_ddm_vars = measure_labels %>%
  filter(overall_difference %in% c("non-contrast", "contrast")) %>%
  select(dv)

@@

```{r message=FALSE}
rel_df %>%
  gather(key, value, -dv, -icc2.1)%>%
  left_join(measure_labels %>% select(dv, task),by="dv") %>%
  ggplot(aes(icc2.1, value))+
  geom_point(aes(col=task))+
  facet_wrap(~key)+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
  xlim(-0.5, 1)+
  ylim(-0.5, 1)+
  ylab("")+
  theme(legend.title = element_blank(),
        aspect.ratio = 1)
```

##R1.7
>It is stated on pg. 9 that the ICC ranges from -1 to 1. Though statistical packages report negative ICCs, it is sometimes suggested that they should be treated as zero (e.g. Bartko, 1976), as a proportion of variance cannot theoretically be negative. I am unsure what the best approach is for the current purposes, but I note it for consideration. As there don't appear to be a large number of negative ICCs, I suspect it wouldn't affect the averages much.

TODO:
- report how many negative ICC's there are
- run all analyses that include ICC's with 
  - replacing negative values with 0's 
  - removing them

There are 21 variables with negative point estimate ICC's. This is less than 5% of the measures.

```{r}
rel_df %>%
  mutate(neg_icc = ifelse(icc2.1<0,1,0)) %>%
  summarise(sum_neg = sum(neg_icc))
```

### Replacing negative ICC's with 0's

```{r}
rel_df_rep=rel_df %>%
  select(dv, task, icc2.1) %>%
  mutate(icc2.1=ifelse(icc2.1<0,0,icc2.1))
```

Reliability by task vs survey
```{r}
summary(MCMCglmm(icc2.1 ~ task, data=rel_df_rep, verbose=F))
```

Reliability depending on number of trials
```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(rel_df_rep[,c("dv", "icc2.1")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=F))
```

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1,
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(rel_df_rep[,c("dv", "icc2.1")], by = 'dv')
```

Comparing contrast vs non-contrast: overall has higher reliability than difference.

```{r}
summary(MCMCglmm(icc2.1 ~ contrast, data=tmp, verbose=FALSE))
```

Comparing raw vs ddm in overall estimates

```{r message=FALSE, warning=FALSE}
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "non-contrast"), verbose=FALSE))
```

Comparing raw vs ddm in difference scores

```{r message=FALSE, warning=FALSE}
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
```

### Removing negative ICC's

```{r}
rel_df_ex = rel_df %>%
  select(dv, task, icc2.1) %>%
  filter(icc2.1>0)
```

Reliability by task vs survey
```{r}
summary(MCMCglmm(icc2.1 ~ task, data=rel_df_ex, verbose=F))
```

Reliability depending on number of trials
```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(rel_df_ex[,c("dv", "icc2.1")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=F))
```

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1,
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(rel_df_ex[,c("dv", "icc2.1")], by = 'dv')
```

Comparing contrast vs non-contrast: overall has higher reliability than difference.

```{r}
summary(MCMCglmm(icc2.1 ~ contrast, data=tmp, verbose=FALSE))
```

Comparing raw vs ddm in overall estimates

```{r}
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "non-contrast"), verbose=FALSE))
```

Comparing raw vs ddm in difference scores

```{r}
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
```

@@

##R1.8
>I think it is a strength of the paper overall that the authors consider the importance of trial numbers, though I'm curious why they chose the number of trials they did for their tasks (e.g. if they came from particular studies or an average)? The role of trial numbers was also something we were interested in (see our Supplementary material D: https://link.springer.com/article/10.3758/s13428-017-0935-1#SupplementaryMaterial), and is discussed by Rouder & Haaf (2018).

TODO:
- [DONE] extract trial numbers for papers that went in to the lit search and compare to ours
- code pipeline to get reliability with k number of trials

```{r warning=FALSE, message=FALSE}
tmp1 = lit_review %>%
  filter(task == "task") %>%
  select(dv, total_trial_numbers) %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(mean_num_trials_lit = mean(total_trial_numbers, na.rm=T))

tmp2 = measure_labels %>%
  filter(task == "task") %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(mean_num_trials_emp = mean(num_all_trials))

tmp2 %>%
  left_join(tmp1, by="task_name")
```

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd

tmp2 %>%
  left_join(tmp1, by="task_name")
```

#R2

##R2.1
>The researchers were careful in their sampling procedure to try to minimize differences between participants who completed (vs. did not complete) the retest phase of the test-retest. Some simple statistical comparisons between the completers (N = 157) and non-completers/non-responders (N = 242-157 = 85) would help characterize this subset of the sample better and provide an additional data quality check.

TODO: Compare invited but not completing

```{r warning=FALSE, message=FALSE}
mturk_worker_data = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')

worker_lookup = read_json('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/worker_lookup.json')

worker_lookup = data.frame(worker_lookup) %>%
  gather(sub_id, worker_id)

retest_workers = mturk_worker_data %>%
  select(Worker.ID, CURRENT.RetestWorker, CURRENT.RetestWorkerB2, CURRENT.RetestWorkerB3, CURRENT.RetestWorkerB4, CURRENT.RetestWorkerB5) %>%
  replace(., is.na(.), 0) %>%
  mutate(retest_worker = ifelse(CURRENT.RetestWorker+ CURRENT.RetestWorkerB2+CURRENT.RetestWorkerB3+CURRENT.RetestWorkerB4+ CURRENT.RetestWorkerB5>0,1,0)) %>%
  filter(retest_worker==1) %>%
  select(Worker.ID) %>%
  rename(worker_id = Worker.ID) %>%
  left_join(worker_lookup, by = "worker_id") %>%
  select(-worker_id)
```

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd

tmp2 %>%
  left_join(tmp1, by="task_name")
```

#R2

##R2.1
>The researchers were careful in their sampling procedure to try to minimize differences between participants who completed (vs. did not complete) the retest phase of the test-retest. Some simple statistical comparisons between the completers (N = 157) and non-completers/non-responders (N = 242-157 = 85) would help characterize this subset of the sample better and provide an additional data quality check.

TODO: How many variables are significantly different than each other between the subjects who have been invited and completed the retest battery and those who have not after FDR correcting for multiple comparisons?

```{r warning=FALSE, message=FALSE}
mturk_worker_data = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')

worker_lookup = read_json('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/worker_lookup.json')

worker_lookup = data.frame(worker_lookup) %>%
  gather(sub_id, worker_id)

retest_workers = mturk_worker_data %>%
  select(Worker.ID, CURRENT.RetestWorker, CURRENT.RetestWorkerB2, CURRENT.RetestWorkerB3, CURRENT.RetestWorkerB4, CURRENT.RetestWorkerB5) %>%
  replace(., is.na(.), 0) %>%
  mutate(retest_worker = ifelse(CURRENT.RetestWorker+ CURRENT.RetestWorkerB2+CURRENT.RetestWorkerB3+CURRENT.RetestWorkerB4+ CURRENT.RetestWorkerB5>0,1,0)) %>%
  filter(retest_worker==1) %>%
  select(Worker.ID) %>%
  rename(worker_id = Worker.ID) %>%
  left_join(worker_lookup, by = "worker_id") %>%
  select(-worker_id)

test_data_522 = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/variables_exhaustive.csv')

test_data_522 = test_data_522 %>%
  rename(sub_id = X)

test_data_522_subs = test_data_522$sub_id

test_data_522 <- test_data_522[,names(test_data_522) %in% retest_report_vars]

test_data_522$sub_id = test_data_522_subs

non_completers = retest_workers %>%
  filter(sub_id %in% retest_data$sub_id==FALSE)

completers = retest_data %>%
  select(sub_id)

non_completer_data = test_data_522 %>%
  filter(sub_id %in% non_completers$sub_id)

completer_data = test_data_522 %>%
  filter(sub_id %in% completers$sub_id)

out_df = data.frame(dv=NA, p_val=NA)

for(i in retest_report_vars[-1]){
  x = non_completer_data %>% select(i)
  y = completer_data %>% select(i)
  tmp = data.frame(dv = i, p_val = t.test(x,y)$p.value)
  out_df = rbind(out_df, tmp)
}
out_df = out_df[-1,]

sum(p.adjust(out_df$p_val, method = "fdr") < 0.05)
```

### 2018-12-21 code/analysis_nbs/ResponseToReviewers.Rmd

Comparing raw vs ddm in difference scores

```{r}
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
```

##R1.8
>I think it is a strength of the paper overall that the authors consider the importance of trial numbers, though I'm curious why they chose the number of trials they did for their tasks (e.g. if they came from particular studies or an average)? The role of trial numbers was also something we were interested in (see our Supplementary material D: https://link.springer.com/article/10.3758/s13428-017-0935-1#SupplementaryMaterial), and is discussed by Rouder & Haaf (2018).

TODO:
- [DONE] extract trial numbers for papers that went in to the lit search and compare to ours
- [PARTIALLY DONE] code pipeline to get reliability with k number of trials

@@

```{r warning=FALSE, message=FALSE}
tmp1 = lit_review %>%
  filter(task == "task") %>%
  select(dv, total_trial_numbers) %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(mean_num_trials_lit = mean(total_trial_numbers, na.rm=T))

tmp2 = measure_labels %>%
  filter(task == "task") %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(mean_num_trials_emp = mean(num_all_trials))

tmp2 %>%
  left_join(tmp1, by="task_name")
```

```{r}
script_loader(file='make_rel_df.R', path='SRO_Retest_Analyses/code/helper_functions/')

input_path = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/trial_num/ordered/'

for(i in c(0.25, 0.5, 0.75)){
  df1 = read.csv(paste0(input_path, 'complete_', as.character(i) ,'_variables_exhaustive.csv'))
  df1 = df1 %>% rename(sub_id = X)

  df2 = read.csv(paste0(input_path, 'retest_', as.character(i) ,'_variables_exhaustive.csv'))
  df2 = df2 %>% rename(sub_id = X) %>% 
    filter(sub_id %in% df1$sub_id)

  numeric_cols = get_numeric_cols(df1, df2)

  subs = df1$sub_id

  df1 = df1[,numeric_cols]
  df2 = df2[,numeric_cols]

  df1 = df1 %>%
    select_if(function(col) !is.na(sd(col))) %>%
    select_if(function(col) sd(col) != 0)

  df2 = df2 %>%
    select_if(function(col) !is.na(sd(col))) %>%
    select_if(function(col) sd(col) != 0)

  df1$sub_id = subs
  df2$sub_id = subs

  cur_rel_df = make_rel_df(t1_df=df1, t2_df=df2, metrics = c("icc2.1", "icc3.k", "var_breakdown"))
  cur_rel_df$proptrials = i
  if(!exists('rel_df')){
    rel_df = cur_rel_df
  } else{
    rel_df = rbind(rel_df, cur_rel_df)
  }
}
rm(cur_rel_df)
```

```{r message=FALSE, warning=FALSE}
rel_df %>% 
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  filter(task_name != "columbia_card_task_cold") %>%
  mutate(task_name = factor(task_name, levels = c("columbia_card_task_hot","go_nogo", "hierarchical_rule", "keep_track","kirby", "ravens"),
                            labels = c("Columbia Card Task (24)","Go/No-go (200)","Hierarchical Rule (300)", "Keep Track (9)","Kirby (27)", "Ravens (18)"))) %>%
  ggplot(aes(factor(proptrials), icc2.1, col=task_name, shape=task_name))+
  geom_point(aes(group=dv))+
  geom_line(aes(group=dv))+
  xlab("Proportion of trials")+
  ylab("ICC 2.1")+
  theme(legend.title=element_blank(),
        panel.grid=element_blank())+
  guides(color = guide_legend(nrow=2))+
  scale_color_manual(values=c('#762a83','#af8dc3','#e7d4e8','#d9f0d3','#7fbf7b','#1b7837'))
```

```{r}
summary(MCMCglmm(icc2.1 ~ factor(proptrials), random=~dv, data = rel_df, verbose=FALSE))
```

### 2018-12-21 code/analysis_nbs/ResponseToReviewers.Rmd

There are 21 variables with negative point estimate ICC's. This is less than 5% of the measures.

```{r}
rel_df %>%
  mutate(neg_icc = ifelse(icc2.1<0,1,0)) %>%
  summarise(sum_neg = sum(neg_icc))
```

### Replacing negative ICC's with 0's

```{r}
rel_df_rep=rel_df %>%
  left_join(measure_labels %>% select(dv, task), by="dv") %>%
  select(dv, task, icc2.1) %>%
  mutate(icc2.1=ifelse(icc2.1<0,0,icc2.1))
```

@@

Reliability by task vs survey
```{r}
summary(MCMCglmm(icc2.1 ~ task, data=rel_df_rep, verbose=F))
```

Reliability depending on number of trials
```{r warning=FALSE, message=FALSE}
script_loader('meaningful_vars_data.R', path="SRO_Retest_Analyses/code/workspace_scripts/")

tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(rel_df_rep[,c("dv", "icc2.1")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

@@

Comparing raw vs ddm in difference scores

```{r message=FALSE, warning=FALSE}
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
```

### Removing negative ICC's

```{r}
rel_df_ex = rel_df %>%
  left_join(measure_labels %>% select(dv, task), by="dv") %>%
  select(dv, task, icc2.1) %>%
  filter(icc2.1>0)
```

@@

```{r warning=FALSE, message=FALSE}
tmp1 = lit_review %>%
  filter(task == "task") %>%
  select(dv, total_trial_numbers) %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(mean_num_trials_lit = mean(total_trial_numbers, na.rm=T))

tmp2 = measure_labels %>%
  filter(task == "task") %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.') %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(mean_num_trials_emp = mean(num_all_trials))

tmp2 %>%
  left_join(tmp1, by="task_name")
```

```{r}
rm(rel_df)

script_loader(file='make_rel_df.R', path='SRO_Retest_Analyses/code/helper_functions/')

@@

  subs = df1$sub_id

  df1 = df1[,numeric_cols]
  df2 = df2[,numeric_cols]

  df1 = df1 %>%
    select_if(function(col) !is.na(sd(col))) %>%
    select_if(function(col) sd(col) != 0)

  # df2 = df2 %>%
  #   select_if(function(col) !is.na(sd(col))) %>%
  #   select_if(function(col) sd(col) != 0)

  df2 = df2[,c(names(df1))]

### 2019-01-22 code/SRO_Retest_Analyses.Rmd
rerunning everything with new release

```{r, message=FALSE, warning=FALSE, include=FALSE}
set.seed(10394839)
from_gh = TRUE
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
set.seed(10394839)
from_gh = FALSE
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
```
